Naturalness in U(1) extensions of the MSSM

### 2014-11-12 paper/e6ssm-tuning-paper.tex
Added MSSM RGE approximate solutions to appendix

% macros
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\SuperField}[1]{\hat{#1}}

%\nofiles
% For draft, uncomment to avoid huge spaces
\raggedbottom
%
\begin{document}

@@

the MSSM and may be obtained from general results \cite{Martin:1993zk} for other models.

>>>>

% macros
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\SuperField}[1]{\hat{#1}}
\allowdisplaybreaks
%\nofiles
% For draft, uncomment to avoid huge spaces
\raggedbottom
%
\begin{document}

@@

the MSSM and may be obtained from general results \cite{Martin:1993zk} for other models. To calculate the fine
tuning it is necessary to expand out all of the parameters appearing in the EWSB conditions in terms
of the high scale parameters.\\ \\
In the MSSM, the relevant parameters are $\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$, $m_{Q3}^2$, $m_{u3}^2$ and $A_t$ when
the 1-loop top and stop effective potential terms are included (as no dimensionless couplings are varied
in the fine tuning calculation, we neglect expanding the gauge and Yukawa couplings). For a parameter $p$, the series expansion
Eq. (\ref{eq:rgeapproxsoln}) reads
\begin{equation*}
q(Q)=q(M_X)+\int_0^t q(t')\;\textrm{d}t'\approx q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{(16\pi^2)^2}b_q^{(2)}(M_X),
\end{equation*}
where we have for convenience defined
\begin{equation*}
b_q^{(2)}(M_X)=\frac{1}{2!}\left [ \sum_{q_k}\beta_{q_k}^{(1)}\frac{\partial \beta_q}{\partial q_k}\right ]_{M_X}
\end{equation*}
and the notation $[\ldots]_Q$ indicates that everything within the brackets is evaluated at the scale $Q$. It is straightforward 
to get the explicit series expansions for the MSSM parameters listed above. Due to the smallness of the first and second
generation Yukawa couplings, we neglect them in our calculations. Similarly we neglect the corresponding soft SUSY breaking 
trilinears. Additionally, all soft mass matrices are assumed diagonal, and the gaugino masses are taken to be real.
For the MSSM, we then obtain the following results. For the parameter $\mu$, one has the coefficients
\begin{subequations}\label{eq:mubetas}
\beta_\mu^{(1)}&=\mu\left ( 3y_t^2+3y_b^2+y_\tau^2-3g_2^2-\frac{3}{5}g_1^2\right ),\label{eq:mubeta1}\\
\beta_\mu^{(2)}&=\mu \bigg ( -9y_t^4-9y_b^4-6y_t^2y_b^2-3y_\tau^4+16g_3^2y_t^2+\frac{4}{5}g_1^2y_t^2+16g_3^2y_b^2-\frac{2}{5}g_1^2y_b^2\nonumber\\
&\qquad{}+\frac{6}{5}g_1^2y_\tau^2+\frac{15}{2}g_2^4+\frac{9}{5}g_1^2g_2^2+\frac{207}{50}g_1^4\bigg ),\label{eq:mubeta2}\\
b_\mu^{(2)}&=\frac{\mu}{2}\Bigg [ 45y_t^4+45y_b^4+9y_\tau^2+30y_t^2y_b^2+6y_t^2y_\tau^2+18y_b^2y_\tau^2-32g_3^2(y_t^2+y_b^2)\nonumber\\
&\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ].\label{eq:mub2}
The coefficients for $B$ are 
\begin{subequations}\label{eq:Bbetas}
\beta_B^{(1)}&=6y_t^2A_t+6y_b^2A_b+2y_\tau^2A_\tau+6g_2^2M_2+\frac{6}{5}g_1^2M_1,\label{eq:Bbeta1}\\
\beta_B^{(2)}&=-36y_t^4A_t-36y_b^4A_b-12y_\tau^4A_\tau-12y_t^2y_b^2(A_t+A_b)+32g_3^2y_t^2(A_t-M_3)\nonumber\\
&\quad{}+32g_3^2y_b^2(A_b-M_3)+\frac{8}{5}g_1^2y_t^2(A_t-M_1)-\frac{4}{5}g_1^2y_b^2(A_b-M_1)+\frac{12}{5}g_1^2y_\tau^2(A_\tau-M_1)\nonumber\\
&\quad{}-30g_2^4M_2-\frac{18}{5}g_1^2g_2^2(M_1+M_2)-\frac{414}{25}g_1^4M_1,\label{eq:Bbeta2}\\
b_B^{(2)}&=72y_t^4A_t+72y_b^4A_b+16y_\tau^4A_\tau+12y_t^2y_b^2(A_t+A_b)+12y_\tau^2y_b^2(A_b+A_\tau)\nonumber\\
&\quad{}-32g_3^2y_t^2(A_t-M_3)-32g_3^2y_b^2(A_b-M_3)\nonumber\\
&\quad{}-18g_2^2y_t^2(A_t-M_2)-18g_2^2y_b^2(A_b-M_2)-6g_2^2y_\tau^2(A_\tau-M_2)\nonumber\\
&\quad{}-\frac{26}{5}g_1^2y_t^2(A_t-M_1)-\frac{14}{5}g_1^2y_b^2(A_b-M_1)-\frac{18}{5}g_1^2y_\tau^2(A_\tau-M_1)\nonumber\\
&\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1.\label{eq:Bb2}
The coefficients for $m_{H_d}^2$ and $m_{H_u}^2$ are 
\begin{subequations}\label{eq:mHd2Betas}
\beta_{m_{H_d}^2}^{(1)}&=6y_b^2\left (m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2 \right )+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2\right )\nonumber\\
&\quad{}-6g_2^2M_2^2-\frac{3}{5}g_1^2\left ( \mathcal{S}+2M_1^2\right ),\label{eq:mHd2beta1}\\
\beta_{m_{H_d}^2}^{(2)}&=-36y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
&\quad{}-6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
&\quad{}-12y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2A_\tau^2\right )\nonumber\\
&\quad{}+32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
&\quad{}+\frac{6}{5}g_1^2y_t^2\left ( 3m_{H_u}^2+m_{Q3}^2-4m_{u3}^2\right )\nonumber\\
&\quad{}-\frac{2}{5}g_1^2y_b^2\left ( 11m_{H_d}^2-m_{Q3}^2-4m_{d3}^2+2A_b^2-4M_1A_b+4M_1^2\right )\nonumber\\
&\quad{}+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+4m_{e3}^2+2A_\tau^2-4M_1A_\tau+4M_1^2\right )\nonumber\\
&\quad{}-\frac{16}{5}g_3^2g_1^2\left (\sum_{i=1}^3 m_{Qi}^2-2m_{ui}^2+m_{di}^2 \right )\nonumber\\
&\quad{}+3g_2^4\left ( 11M_2^2+m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3 [3m_{Qi}^2+m_{Li}^2]\right )\nonumber\\
&\quad{}+\frac{9}{5}g_1^2g_2^2\left ( 2M_1^2+2M_2^2+2M_1M_2-m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3[m_{Li}^2-m_{Qi}^2]\right )\nonumber\\
&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_d}^2+\sum_{i=1}^3[18m_{Li}^2+2m_{Qi}^2+56m_{ui}^2+2m_{di}^2-18m_{ei}^2]\right ),\label{eq:mHd2beta2}\\
b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
&\quad{}+12y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{d3}^2+m_{L3}^2+m_{e3}^2+(A_\tau+A_b)^2\right )\nonumber\\
&\quad{}+16y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2A_\tau^2\right )\nonumber\\
&\quad{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
&\quad{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
&\quad{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2-2M_2A_\tau+2M_2^2\right )\nonumber\\
&\quad{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
&\quad{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2-2M_1A_\tau+2M_1^2\right )\nonumber\\
&\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:mHd2b2}
\begin{subequations}\label{eq:mHu2Betas}
\beta_{m_{H_u}^2}^{(1)}&=6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-6g_2^2M_2^2+\frac{3}{5}g_1^2\left ( \mathcal{S}-2M_1^2\right ),\label{eq:mHu2beta1}\\
\beta_{m_{H_u}^2}^{(2)}&=-36y_t^4(m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2)\nonumber\\
&\quad{}-6y_t^2y_b^2(m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2)\nonumber\\
&\quad{}+32g_3^2y_t^2(m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_3+2M_3^2)\nonumber\\
&\quad{}+\frac{2}{5}g_1^2y_t^2(-5m_{H_u}^2+m_{Q3}^2+16m_{u3}^2+4A_t^2-8A_tM_1+8M_1^2)\nonumber\\
&\quad{}+\frac{6}{5}g_1^2y_b^2(3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2)+\frac{6}{5}g_1^2y_\tau^2(m_{H_d}^2+m_{L3}^2-2m_{e3}^2)\nonumber\\
&\quad{}+\frac{16}{5}g_1^2g_3^2\left(\sum_{i=1}^3m_{Qi}^2-2m_{ui}^2+m_{di}^2\right )\nonumber\\
&\quad{}+\frac{9}{5}g_1^2g_2^2\left ( 2M_2^2+2M_1^2+2M_1M_2+m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3m_{Qi}^2-m_{Li}^2\right )\nonumber\\
&\quad{}+3g_2^4\left ( 11M_2^2+m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3[3m_{Qi}^2+m_{Li}^2]\right )\nonumber\\
&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_u}^2+\sum_{i=1}^3[4m_{Qi}^2-8m_{ui}^2+10m_{di}^2+54m_{ei}^2]\right ),\label{eq:mHu2beta2}\\
b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
&\quad{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_3+2M_3^2\right )\nonumber\\
&\quad{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_2+2M_2^2\right )\nonumber\\
&\quad{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_1+2M_1^2\right )\nonumber\\
&\quad{}+\frac{198}{25}g_1^4\left ( \mathcal{S}-3M_1^2\right )-18g_2^4M_2^2.\label{eq:mHu2b2}
In these expressions the quantity $\mathcal{S}$ is defined by
\begin{equation}\label{eq:gaugeBetaContribution}
\mathcal{S}=m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2\right ).
If additional loop corrections are included from the 1-loop effective potential, it is also
necessary to construct the expansions for $m_{Q3}^2$, $m_{u3}^2$ and $A_t$. The coefficients for $m_{Q3}^2$ and
$m_{u3}^2$ are
\begin{subequations}\label{eq:mq32Betas}
\beta_{m_{Q3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )+2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2\right )\\
&\quad{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2+\frac{1}{5}g_1^2\left ( \mathcal{S}-\frac{2}{3}M_1^2\right ),\label{eq:mQ32beta1}\\
\beta_{m_{Q3}^2}^{(2)}&=-20y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )-20y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
&\quad{}-2y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{L3}^2+m_{d3}^2+m_{e3}^2+(A_b+A_\tau)^2\right )\nonumber\\
&\quad{}+\frac{2}{5}g_1^2y_t^2\left ( m_{H_u}^2+3m_{Q3}^2+8m_{u3}^2+4A_t^2-8A_tM_1+8M_1^2\right )\nonumber\\
&\quad{}+\frac{2}{5}g_1^2y_b^2\left ( 5m_{H_d}^2+m_{Q3}^2+2A_b^2-4A_bM_1+4M_1^2\right )\nonumber\\
&\quad{}+\frac{2}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
&\quad{}+\frac{16}{3}g_3^4\left ( \sum_{i=1}^3 \left [ 2m_{Qi}^2+m_{ui}^2+m_{di}^2\right ]-8M_3^2\right )\nonumber\\
&\quad{}+32g_3^2g_2^2\left ( M_2^2+M_3^2+M_2M_3\right )\nonumber\\
&\quad{}+\frac{16}{45}g_3^2g_1^2\left ( 3\sum_{i=1}^3\left [ m_{Qi}^2-2m_{ui}^2+m_{di}^2\right ]+2M_1^2+2M_3^2+2M_1M_3\right )\nonumber\\
&\quad{}+3g_2^4\left ( m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+m_{Li}^2\right ]+11M_2^2\right )\nonumber\\
&\quad{}+\frac{1}{5}g_1^2g_2^2\left ( 2M_1^2+2M_2^2+2M_1M_2+3m_{H_u}^2-3m_{H_d}^2+3\sum_{i=1}^3\left [ m_{Qi}^2-m_{Li}^2\right ]\right )\nonumber\\
&\quad{}+\frac{1}{75}g_1^4\bigg ( 199M_1^2+12m_{H_u}^2-6m_{H_d}^2\nonumber\\
&\qquad\qquad\qquad{}+\sum_{i=1}^3\left [ 2m_{Qi}^2-6m_{Li}^2-24m_{ui}^2+6m_{di}^2+42m_{ei}^2\right ]\bigg ),\label{eq:mQ32beta2}\\
b_{m_{Q3}^2}^{(2)}&=24y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
&\quad{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{L3}^2+m_{d3}^2+m_{e3}^2+(A_b+A_\tau)^2\right )\nonumber\\
&\quad{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
&\quad{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
&\quad{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
&\quad{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
&\quad{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
&\quad{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
&\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:mQ32b2}
\begin{subequations} \label{eq:mu32Betas}
\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-\frac{32}{3}g_3^2M_3^2-\frac{4}{5}g_1^2\left ( \mathcal{S}+\frac{8}{3}M_1^2\right ),\label{eq:mu32beta1}\\
\beta_{m_{u3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
&\quad{}-4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
&\quad{}+12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
&\quad{}-\frac{4}{5}g_1^2y_t^2\left ( 9m_{u3}^2-5m_{H_u}^2-m_{Q3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
&\quad{}-\frac{8}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )-\frac{8}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
&\quad{}+\frac{16}{3}g_3^4\left ( \sum_{i=1}^3\left [2m_{Qi}^2+m_{ui}^2+m_{di}^2 \right ]-8M_3^2\right )\nonumber\\
&\quad{}+\frac{64}{45}g_3^2g_1^2\left ( 8M_1^2+8M_3^2+8M_1M_3-3\sum_{i=1}^3\left [ m_{Qi}^2-2m_{ui}^2+m_{di}^2\right ]\right )\nonumber\\
&\quad{}-\frac{12}{5}g_1^2g_2^2\left ( m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left [ m_{Qi}^2-m_{Li}^2\right ]\right )\nonumber\\
&\quad{}+\frac{4}{75}g_1^4\left ( 856M_1^2+3m_{H_u}^2+21m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+21m_{Li}^2+64m_{ui}^2+4m_{di}^2-12m_{ei}^2\right ]\right ),\label{eq:mu32beta2}\\
b_{m_{u3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
&\quad{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
&\quad{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
&\quad{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
&\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ).\label{eq:mu32b2}
Finally, the coefficients for $A_t$ read
\begin{subequations}\label{eq:AtBetas}
\beta_{A_t}^{(1)}&=12y_t^2A_t+2y_b^2A_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1,\label{eq:Atbeta1}\\
\beta_{A_t}^{(2)}&=-88y_t^4A_t-20y_b^4A_b-10y_t^2y_b^2(A_t+A_b)-2y_b^2y_\tau^2(A_b+A_\tau)\nonumber\\
&\quad{}+32g_3^2y_t^2(A_t-M_3)+12g_2^2y_t^2(A_t-M_2)+\frac{12}{5}g_1^2y_t^2(A_t-M_1)+\frac{4}{5}g_1^2y_b^2(A_b-M_1)\nonumber\\
& \quad{}+\frac{64}{9}g_3^4M_3-16g_3^2g_2^2(M_2+M_3)-\frac{272}{45}g_3^2g_1^2(M_1+M_3)-30g_2^4M_2\nonumber\\
&\quad{}-2g_2^2g_1^2(M_1+M_2)-\frac{5486}{225}g_1^4M_1,\label{eq:Atbeta2}\\
b_{A_t}^{(2)}&=144y_t^4A_t+24y_b^4A_b+14y_t^2y_b^2(A_t+A_b)+2y_b^2y_\tau^2(A_b+A_\tau)\nonumber\\
&\quad{}-64g_3^2y_t^2(A_t-M_3)-36g_2^2y_t^2(A_t-M_2)-\frac{52}{5}g_1^2y_t^2(A_t-M_1)\nonumber\\
&\quad{}-\frac{32}{3}g_3^2y_b^2(A_b-M_3)-6g_2^2y_b^2(A_b-M_2)-\frac{14}{15}g_1^2y_b^2(A_b-M_1)\nonumber\\
&\quad{}-64g_3^4M_3+12g_2^4M_2+\frac{572}{25}g_1^4M_1.\label{eq:Atb2}
It is then trivial to extract the relevant terms for the fine tuning calculation in the MSSM from these expressions.\\ \\
In $U(1)$ extended models the 2-loop RGEs are lengthy even if $U(1)$ mixing effects are
neglected. As for the MSSM, we present simplified expressions in which it is assumed that the first and 
second generation Yukawas are zero along with the soft SUSY breaking trilinears.
